Effect of character correlation

### 2018-03-27 Analysis/03-EffectCorrelationFigure.Rmd
Updated figures pipeline

```{r, eval = FALSE, echo = FALSE}
pdf("../Writing/Figures/RF_results_best.pdf",width = 8,height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "RF for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "best", ylab = "RF for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "best",
    ylab = "RF for 150 taxa", NTS = TRUE)
par(op)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf("../Writing/Figures/Tr_results_best.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "Tr for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "best", ylab = "Tr for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "best",
    ylab = "Tr for 150 taxa", NTS = TRUE)
par(op)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf("../Writing/Figures/RF_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "RF for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "null", ylab = "RF for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "null",
    ylab = "RF for 150 taxa", NTS = TRUE)
par(op)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf("../Writing/Figures/Tr_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "null",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "Tr for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "null", ylab = "Tr for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "null",
    ylab = "Tr for 150 taxa", NTS = TRUE)
par(op)
dev.off()
```

>>>>

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/RF_results_best.pdf",width = 8,height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "RF for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "best", ylab = "RF for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "best",
    ylab = "RF for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/Tr_results_best.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "best",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "Tr for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "best", ylab = "Tr for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "best",
    ylab = "Tr for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/RF_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 2, what = "null",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "RF for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "null", ylab = "RF for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "null",
    ylab = "RF for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, result = 'hide'}
pdf("../Writing/Figures/Tr_results_null.pdf", width = 8, height = 8)
op <- par(mfrow=c(3,1), mar = c(2, 4, 1, 2))
plot.results.single(t25_list, metric = 4, what = "null",
    legend = FALSE, NTS = TRUE, xlab = "", ylab = "Tr for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 4, what = "null", ylab = "Tr for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 4, what = "null",
    ylab = "Tr for 150 taxa", NTS = TRUE)
par(op)
# dev.off()
```
